---
title: "113-2 Sneaker Analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup} 
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
{
stars <- function(beta, pval, sig=2, zero = 2) {
  #(print("in stars"))
  st <- function(p){
      if (is.na(p))
        r <- "NA"
      else {
        if (p<0.001)     r <- "***"
        else if (p<0.01) r <- "** "
        else if (p<0.05) r <- "*  "
        else if (p<0.1)  r <- ".  "
        else r <- "   "    
      }
  }
  # round2 <- function(val,sig) {
  #   ret <- paste0(round(beta,sig))
  #   paste0(ret,paste0(rep_len("0",sig),collapse=""))
  # }
    
  if (is.matrix(beta) | is.vector(beta))
  {
    ret <- mapply( FUN = function(beta,pval,sig){
      # paste0(round(beta,sig),st(pval)) }, 
      paste0(format(round(beta,sig),nsmall=zero),st(pval)) }, 
          beta, pval, sig)
    beta[] <- ret
    return(data.frame(beta))
  }
  else {
    #paste0(round(beta,sig),nsmall=zero,st(pval))
    paste0(format(round(beta,sig),nsmall=zero),st(pval))
  }
}

corr <- function(x,y=NULL,type="pearson",sort=FALSE,kable=FALSE)
#type=c("pearson","spearman")
{
  # y <- tolCountrysum
  # x <- GLOLCA$posterior 
  # type="pearson"
  
  #biserialresult <- biserial(y,x) #continuous y variable and a dichotmous x variable
  
  if(is.null(y)) {
    ret <- Hmisc::rcorr(as.matrix(data.frame(x)),type=type)
    
    r <- ret$r
    p <- ret$P
  }

  else {
    ret <- Hmisc::rcorr(as.matrix(data.frame(x,y)),type=type)
    dim <- 1
    if(!is.null(ncol(x)))
      dim <- 1:ncol(x)

    r <- ret$r[-dim,dim]
    p <- ret$P[-dim,dim]
  }

  
  
  #ret2 <- cbind(stars(r,p), PopulationMean=apply(y, MARGIN = 2, FUN = weighted.mean, SES$weights))
  ret2 <- stars(r,p)      
  
  if(sort == TRUE){
      maxGroup <- apply(r,1,which.max)
      
      order <- rep(1,nrow(r))

      for (x in unique(maxGroup)) {
         order[maxGroup == x] <- r[maxGroup == x,x]
      }

      # order <-  ifelse(maxGroup==1,r[,1],
      #           ifelse(maxGroup==2,r[,2],
      #           ifelse(maxGroup==3,r[,3],
      #           ifelse(maxGroup==4,r[,4],NA))))

      ret2 <- ret2[order(maxGroup,-order),]
  }

  if(kable == TRUE){
      (kable(ret2,#[order(r[,2]),],
        caption = "corr: Tol not extend to SEA
        Spearman correlation for tolerance is not normal", digits = 2))
  } else
    ret2

}

reg <- function (Y, X, formula=NULL, data=NULL, model = "lm", sig=3, 
                 addCoef=NULL, addPVal=NULL, addAnova=NULL, sortBy=NULL,
                 weights=NULL, subset=NULL, caption = NULL,
                 addSE=TRUE, addFit=TRUE,unstar=FALSE, simpleReg=FALSE, suppressByPVal=FALSE, long=T, kable=TRUE) 
#sortBy = sort by "colname" (e.g. "r2 adj","r2"), or column number.
{
  #addCoef such as "Pr(>|t|)", "Estimate"
  #for debug
  # model = "lm"; sig=3; addSE=TRUE; addFit=TRUE; formula=NULL;
  # kable=TRUE; addCoef=NULL; addPVal=NULL; addAnova=NULL; sortBy=NULL; long=F; addRSQ=T
  # suppressByPVal=FALSE; weights=NULL; unstar=FALSE; subset=NULL; transpose=NULL; caption = NULL
  

  
  regstars <- function(p, val = NULL, simplify = TRUE, stars = TRUE){
    if (is.na(p))
      r <- "NA"
    else {
      if (p<0.001)     r <- "***"
      else if (p<0.01) r <- "** "
      else if (p<0.05) r <- "*  "
      else if (p<0.1)  r <- ".  "
      else r <- "   "    
    }
    
    
    if (!is.null(val) & simplify == TRUE) {
      if (val > 0 & r != "")      r <- paste0("+",r)
      else if (val < 0 & r != "") r <- paste0("-",r)
    }
    else if (!is.null(val) & simplify == FALSE){
      r <- paste0(round(val,3),r)
    }
    
    if (stars == FALSE)
      r <- ""#p
    return (r)
  }
  
  runlm <- function( y, formula, data, model, sig, addSE, addRSQ=T, addCoef, addPVal, addAnova, addFit) {
    #for debug:
    #y=Y[,1]
    

    newdata <- data.frame(data, y=y) #,weights=weights)

    if (model == "lm") {
      # a <- summary(lm    ( formula , data=newdata, weights=weights))  
      # b <- car::Anova  (lm    ( formula , data=newdata, weights=weights),type=2)
      #(print("before lm"))
      #(str(weights))
      mod <- lm ( formula , data=newdata, weights=weights)
      #(print("inside lm"))
      a <- summary(mod)
      #(print("post lm"))
      b <- car::Anova(mod,type=2)
    } else if (model == "nb") {
      a <- summary(MASS::glm.nb( formula , data=newdata, weights=weights) )  
    } else if (model == "lr") {
      mod <-        glm   ( formula , data=newdata, weights=weights, family=binomial(link="logit"))
      a <- summary(mod)
      b <- car::Anova (mod, type=2, test.statistic="LR") #test.statistic="LR", "Wald", "F"
    } else if (model == "poisson") {
      a <- summary(glm   ( formula , data=newdata, weights=weights, family=poisson(link="log")))  
    } else if (model == "or") {
      a <- summary(ordinal::clm   ( formula, data=newdata, weights=weights))
    } else if (model == "lme") {
      a <- summary(lme   ( formula, data=newdata, random = ~1|City, na.action=na.exclude))
      a$coefficients <- a$tTable
      colnames(a$coefficients) <- c("Estimate","Std. Error","DF","t-value","Pr")
    }
    
    #(print("after all lm"))
    #a <- summary(lm( Pn$M46.OperaPek~SES$Gender)) #for bedug
    #a <- summary(glm( MUSIC_Likes$M46.OperaPek~SES$Gender,family=binomial(link="logit"))) #for bedug
    
    if (unstar==TRUE) {
      ret <- as.data.frame(t(a$coefficients[,"Estimate"]))
      name <- colnames(ret)
      ret <- cbind(ret,t(a$coefficients[,grep("^Pr", colnames(a$coefficients))]))
      colnames(ret) <- c(name, paste0("p-",name)) 
    } else {
      #(print("before star"))
      ret <- data.frame( #mapply passes same index of both args to FUN
         # t(mapply(FUN = function(beta,pval,sig){paste0(format(round(beta,sig),nsmall=sig),regstars(pval)) },
         #                 a$coefficients[,"Estimate"],
         #         a$coefficients[,grep("^Pr", colnames(a$coefficients))],
         #         sig))
         t(stars(a$coefficients[,"Estimate"],
                 a$coefficients[,grep("^Pr", colnames(a$coefficients))],
                 sig,sig))
      )
      names(ret) <- rownames(a$coefficients)
      #(print("after star"))
      ret <- ret[,c(2:ncol(ret),1)] #intercept appears last
    }
    #In either case, ret has been created
    
    
    if (addSE){
      SE <- t( paste0("(",format(round(a$coefficients[,"Std. Error"],sig),nsmall=sig),")"))
      colnames(SE) <- colnames(t( a$coefficients[,"Std. Error"]))
      
      SE <- SE[,c(2:ncol(SE),1)] #intercept appears last
      
      #Combine in alternation
      temp <- cbind(ret[1], SE[1])
      for (i in 2:nrow(a$coefficients)){
        temp <- cbind(temp,ret[i], SE[i])
      }
      ret <- temp
    }
    
    
    if (isTRUE(addFit)) {
      if (model == "lm") {
        ret <- cbind(ret,
                     r2     = round(a$r.squared,3), 
                     adj.r2 = round(a$adj.r.squared,3),
                     n = length(resid(a))
        )       
      } else if (model == "nb") {
        ret <- cbind(ret,
                     #r.squared     = round(a$r.squared,3), 
                     AIC = round (a$aic, sig),
                     loglikelihood = round(a$twologlik,sig),
                     n = length(a$deviance.resid)
        )      
      } else if (model == "poisson") {
        ret <- cbind(ret,
                     #r.squared     = round(a$r.squared,3), 
                     AIC = round (a$aic, sig),
                     n = length(a$deviance.resid)
        )   
      } else if (model == "lr") {
        ret <- cbind(ret,
                     #r.squared     = round(a$r.squared,3), 
                     AIC = round (a$aic, sig),
                     n = length(a$deviance.resid) #length(resid(a))
        )      
      }
    }
    
    if (!is.null(addCoef))
      ret <- cbind(ret, Coef = a$coefficients[,"Estimate"][nrow(a$coefficients)])
    #a$coefficients[,addCoef][length(a$coefficients[,addCoef])])
    
    if (!is.null(addPVal))
      if (model == "lm") {
        ret <- cbind(ret, 
                     t      = t(a$coefficients[,grep("^Pr", colnames(a$coefficients))])

        )
      }else {
        ret <- cbind(ret, 
                     t      = t(a$coefficients[,grep("^Pr", colnames(a$coefficients))])
        )
      }
    
    if (!is.null(addAnova))
      if (model == "lm") {
        F <- b$`F value`[1:(length(b$`F value`)-1)]
        P <- b$`Pr(>F)`[1:(length(b$`F value`)-1)]
        names(F) <- names(P) <- attr(a$terms,"term.labels")

        
        ret <- data.frame(t(mapply(
          FUN = function(beta,pval,sig){paste0(round(beta,sig),regstars(pval,stars = !unstar)) },  #1: "0.02***"
          F,
          P,
          sig)))
        
        
        # ret <- data.frame(#cbind(ret, 
        #              F      = t(F),
        #              'Pr(>F)'= t(P),
        #              'Pf'   = t(st),
        #              check.names=FALSE
        # )
      } 
    else if (model == "lr") {
      
      temp <- names(ret)#
      
      ret <- data.frame(t(c(
        mapply(FUN = function( beta,pval,sig){
          paste0(round(beta,sig), regstars(pval,stars = !unstar))      },
          b$`LR Chisq`, b$`Pr(>Chisq)`, sig),     #1: "0.02***"
        b$Df
      )),
      ret)
      
      names(ret) <- c(paste0("LRChisq",rownames(b)),
                      paste0("Df",rownames(b)),
                      temp)
      
      if (!is.null(addPVal)) {
        temp <- names(ret)   #a shorter vector
        ret <- data.frame(t(unlist(b)),ret) 
        names(ret) <- c( paste0(names(unlist(b))," ",rownames(b)), temp) #a longer vector
      }
    }
    
    
    ret 
  }
  
  runlmIND <- function(y, formula, data, model, sig, addSE, addRSQ, addCoef, addPVal, addAnova) {

    t <- terms(formula)

    #The first term
    temp <- runlm(y,t[1], data, model, sig, addSE, addRSQ, addCoef, addPVal, addAnova, addFit=F)
    ret <- temp [1: (length(temp)-2)]  #Remove the intercept
    
    for( i in 2:length(attr(t,"term.labels"))) {  # -1 because y is a term
      temp <- runlm(y,t[i], data, model, sig, addSE, addRSQ, addCoef, addPVal, addAnova, addFit=F)
      ret <- data.frame(ret,
                   temp[1: (length(temp)-2)] ,
                   check.names = F)
    }
    ret
  }
  
  if(!is.data.frame(Y)) #Wrapper so that function can also take a single vector
    Y <- data.frame(Y)


  if (is.null(weights)){
    # weights=rep(1,NROW(Y))  #weights=1 #
    data$weights=rep(1,NROW(Y))  #weights=1 #
  }
  
  if(!is.null(subset)) {
    Y <- subset(Y,subset)
    data <- subset(data,subset)
    # weights <- subset(weights,subset)
  }
  
  if (is.null(formula)) {
    if(!is.data.frame(X)) #Wrapper so that function can also take a single vector
      X <- data.frame(X)
    
    formula <- reformulate(names(X), response = "y")
    data <- data.frame(X,Y)
  }
  
  if (simpleReg == T) {
    ret <- do.call(rbind,lapply(X = Y, formula, FUN = runlmIND, data, model, sig, addSE, addRSQ, addCoef, addPVal, addAnova))
  } else {
    ret <- do.call(rbind,lapply(X = Y, formula, FUN = runlm, data, model, sig, addSE, addRSQ, addCoef, addPVal, addAnova, addFit))  #for each row (each element of Y), call function #, weights
  }
    


  
  if (!is.null(sortBy)) {
    if (is.numeric(sortBy)) {
      if (sortBy < 0) {
        ret <- ret[order( ret[, abs(sortBy)]),]
      } else if (sortBy > 0) {
        ret <- ret[order(-ret[, sortBy]),]
      } else
        warning("sortBy = 0: cannot sort")
    }
    if (is.character(sortBy)) {
      if (sortBy %in% colnames(ret))
      { #handles columns which has been starred and turned into text
        # ret <- ret[order( -as.numeric(gsub("*","",ret[, which(colnames(ret)==sortBy)],fixed=T))),]
        temp <- gsub("*","",ret[, which(colnames(ret)==sortBy)],fixed=T)
        temp <- gsub(".","",temp,fixed=T)
        ret <- ret[order( -as.numeric(temp)),]
                
                
      } else
        warning("No such column in sortBy")
    }
  }
  
  #as.numeric(gsub("*","","0.031***",fixed=T))
  
  if (suppressByPVal==TRUE & !is.null(addPVal)) 
    ret <- ret[ret[, "PVal"]<0.05,]
  
  # if(is.null(kable)) {
  #   ret
  # }  else if(!is.null(transpose)) {
  #   (kable(t(ret),align = 'r', caption=caption))
  # } else
  #   (kable(ret,align = 'r', caption=caption)) 
  
  if(isTRUE(long)) {
    ret <- t(ret)
  }
  
  if(!isTRUE(kable)) {
    ret
  }
  else
    (kable(ret,align = 'r', caption=caption)) 
}
}
```


# Loading and Cleaning Data
```{r load, echo=FALSE, message = FALSE}
DATA <- read.csv("113-2 Questionnaire.csv")
#colnames(DATA)

brands <- c("Nike","Adidas","Puma","NewBalance","Mizuno",
            "Vans","UnderArmour","ASICS","Converse","Brooks")
brands_neworder <- rev(c("Nike","Adidas","NewBalance","Converse",
                     "Puma","ASICS","Vans", "UnderArmour", "Mizuno", "Brooks")) #Based on consideration
attributes <- data.frame(c("High Price 高價","Low Price 低價"),
                       c("Performance-focused 性能導向","Fashion-focused 時尚導向"),
                       c("Heritage 傳統","Modern 現代"),
                       c("Mass-market 大眾","Niche 小眾"),
                       c("Luxury 奢華","Budget 實惠"),
                       c("Japanese 日系","Not Japanese 非日系"),
                       c("Trendy 時尚","Timeless classic 經典"),
                       c("Streetwear 街頭風格","Sportswear 運動風格"),
                       c("Retro aesthetic 復古設計","Futuristic 未來設計"),
                       c("Basketball 籃球專業","Running 跑步專業"),
                       c("Casual 休閒穿搭","Performance 運動性能"),
                       c("Minimalist 極簡設計","Bold 大膽設計"),
                       c("Durability 耐用優先","Style-focused 風格優先"),
                       c("Widespread availability 廣泛供應","Exclusive/limited edition 限量發售"))
colnames(attributes) <- paste0("Attribute",rep(1:14))



#

convert_num <- function(df) {
  df[] <- lapply(df, function(col) {
    col[col == "7-9"] <- "8"  # Replace "7-9" with "8"
    col[col == "4-6"] <- "7"  
    col[col == "≥10"] <- "15"  
    as.numeric(col)  # Convert to numeric
  })
  colnames(df) <- brands
  return(df)
}
Usage1Owned    <- convert_num(DATA[,14:(14+9)])
Usage2Owning   <- convert_num(DATA[,24:(24+9)])
Usage3Consider <- as.data.frame(ifelse(DATA[,4:(4+9)]=="Would consider",1,0))
colnames(Usage3Consider) <- brands


Usage1Owned$type    <- "1.Owned"
Usage2Owning$type <- "2.CurrentlyOwn"
Usage3Consider$type <- "3.Consider"

Funnel <- rbind(Usage1Owned, Usage2Owning, Usage3Consider)
rm(Usage1Owned, Usage2Owning, Usage3Consider)

#
convert_price <- function(df) {
  df[] <- lapply(df, function(col) {
    col[col == "< NT$1000 (US $<30)"] <- "500"  # Replace 
    col[col == "NT$1000-1999 (US$30-59)"] <- "1500"  
    col[col == "NT$2000-2999 (US$60-89)"] <- "2500"  
    col[col == "NT$3000-3999 (US$90-119)"] <- "3500"  
    col[col == "NT$4000-4999 (US$120-149)"] <- "4500"  
    col[col == "NT$5000-6999 (US$150-219)"] <- "6000"  
    col[col == ">NT$7000 (>US$210)"] <- "8000"                  
    as.numeric(col)  # Convert to numeric
  })
  colnames(df) <- brands
  return(df)
}
BrandPrice    <- convert_price(DATA[,34:(34+9)])

#
convert_Likert <- function(df,index) {
  left  <- attributes[1,index]
  right <- attributes[2,index]
  
  df[] <- lapply(df, function(col) {
    col[col == left]     <- "+2"  # Replace 
    col[col == "<"]      <- "1"  
    col[col == "Middle"] <- "0"  
    col[col == ">"]      <- "-1"  
    col[col == right]    <- "-2"               
    as.numeric(col)  # Convert to numeric
  })
  colnames(df) <- brands
  df$attributes <- paste0(formatC(index, width = 2, flag = "0"),". ", left,"(+) vs ",right,"(-)")
  return(df)
}
Brand <- rbind(
  convert_Likert(DATA[,44:(44+9)], 1),
  convert_Likert(DATA[,54:(54+9)], 2),
  convert_Likert(DATA[,64:(64+9)], 3),
  convert_Likert(DATA[,74:(74+9)], 4),
  convert_Likert(DATA[,84:(84+9)], 5),
  convert_Likert(DATA[,94:(94+9)], 6),
  convert_Likert(DATA[,104:(104+9)], 7),
  convert_Likert(DATA[,114:(114+9)], 8),
  convert_Likert(DATA[,124:(124+9)], 9),
  convert_Likert(DATA[,134:(134+9)], 10),
  convert_Likert(DATA[,144:(144+9)], 11),
  convert_Likert(DATA[,154:(154+9)], 12),
  convert_Likert(DATA[,164:(164+9)], 13),
  convert_Likert(DATA[,174:(174+9)], 14)
)
attribute_labels <- unique(Brand$attributes)

#PurchaseCriteria
convert_purchaseCriteria <- function(df) {
  df[] <- lapply(df, function(col) {
    col[col == "Strongly Left"] <- "2"  # Replace 
    col[col == "Slightly Left"] <- "1"  
    col[col == "Middle"] <- "0"  
    col[col == "Slightly Right"] <- "-1"  
    col[col == "Strongly Right"] <- "-2"               
    as.numeric(col)  # Convert to numeric
  })
  colnames(df) <- paste0("criteria",1:14)
  return(df)
}
PurchaseCriteria <- convert_purchaseCriteria(DATA[,184:197])
colnames(PurchaseCriteria) <- attribute_labels
#
Respondent <- data.frame(
              email = DATA[,2],
              studentid = DATA[,3],
              TotalSpendingC = DATA[,198],
              PurchasePYearC = DATA[,199],
              Region = DATA[,200],
              Student = DATA[,201],
              Gender = DATA[,202],
              AgeC = DATA[,203])
Respondent$TotalSpending <- ifelse(Respondent$TotalSpendingC =="NT$0 (US$0)",0,
                            ifelse(Respondent$TotalSpendingC =="NT$0-1999 (US$0-59)",1000,
                            ifelse(Respondent$TotalSpendingC =="NT$2000-4999 (US$60-149)",3500,
                            ifelse(Respondent$TotalSpendingC =="NT$5000-9999 (US$150-299)",7500,
                            ifelse(Respondent$TotalSpendingC =="NT$10000-19999 (US$300-599)",15000,
                            ifelse(Respondent$TotalSpendingC =="NT$20000-39999 (US$600-1199)",25000,
                            ifelse(Respondent$TotalSpendingC =="NT$40000-79999 (US$1200-2399)",60000,
                            ifelse(Respondent$TotalSpendingC ==">NT$80000 (US$2400)",90000,NA))))))))

Respondent$PurchasePYear <- ifelse(Respondent$PurchasePYearC =="0",0,
                            ifelse(Respondent$PurchasePYearC =="1",1,
                            ifelse(Respondent$PurchasePYearC =="2",2,
                            ifelse(Respondent$PurchasePYearC =="3-4",3.5,
                            ifelse(Respondent$PurchasePYearC =="5-6",5.5,
                            ifelse(Respondent$PurchasePYearC =="7-9",8,
                            ifelse(Respondent$PurchasePYearC =="10-12",11,
                            ifelse(Respondent$PurchasePYearC ==">12",13,NA))))))))

Respondent$Age <-           ifelse(Respondent$AgeC =="<18",NA,
                            ifelse(Respondent$AgeC =="18",18,
                            ifelse(Respondent$AgeC =="19",19,
                            ifelse(Respondent$AgeC =="20",20,
                            ifelse(Respondent$AgeC =="21",21,
                            ifelse(Respondent$AgeC =="22",22,
                            ifelse(Respondent$AgeC =="23",23,
                            ifelse(Respondent$AgeC =="24",24,
                            ifelse(Respondent$AgeC =="25-27",26,       
                            ifelse(Respondent$AgeC =="28-30",29,         
                            ifelse(Respondent$AgeC =="≥31",32,NA  )))))))))))
```

# Descriptive Statistics
## Funnel
```{r, echo=FALSE, message = FALSE}
library(ggplot2)
library(showtext)
library(knitr)
showtext_auto()

#Funnel
Funnel_long <- reshape2::melt(Funnel, id.vars=c("type"),variable.name = "brands", value.name = "val")
plotdata <- aggregate( val  ~ . , data=Funnel_long, mean)
plotdata$brands <- factor(plotdata$brands, levels=brands_neworder)
ggplot(data = plotdata, aes(y=brands, x=val)) +
  geom_col() + facet_wrap(vars(type),scales="free_x") +
  labs(title = "Number of sneakers ever owned, currently owned, 
  and percentage of persons who'd consider the brand")
kable(reshape2::dcast(plotdata, brands ~ type,value.var = "val"),digits = 2)

```

## Brand Price
```{r, echo=FALSE, message = FALSE }

plotdata <- data.frame(Brand = brands, Price = colMeans(BrandPrice))
plotdata$Brand <- factor(plotdata$Brand, levels=brands_neworder)
ggplot(data=plotdata, aes(y=Brand, x=Price)) +
  geom_col() + 
  labs(title = "Perceived price of each brand (NTD)") 
kable(plotdata,digits = 2)
```

## Brand Perception
```{r, echo=FALSE, message = FALSE, fig.height=20, fig.width=10}
Brand_long <- reshape2::melt(Brand, id.vars=c("attributes"),variable.name = "brands", value.name = "val")

Brand_long <- rbind(Brand_long,
                    data.frame(attributes=attribute_labels,
                               brands="UserPreference",
                               val=colMeans(PurchaseCriteria))
                    )

BrandPerception <- aggregate( val  ~ . , data=Brand_long, mean)
BrandPerception$brands <- factor(BrandPerception$brands, levels=c("UserPreference",brands_neworder))
ggplot(data = BrandPerception, aes(y=brands, x=val)) +
  geom_col() + facet_wrap(vars(attributes), ncol=2)

kable(reshape2::dcast(BrandPerception, attributes ~ brands),digits = 2)


```



## User Behavior
```{r, echo=FALSE, message = FALSE }
knitr::kable(data.frame(SpendingPerYear=mean(Respondent$TotalSpending),
           PurchasesPerYear=mean(Respondent$PurchasePYear)))
```

# 1.FA on brands
``` {r FAb, eval=T, echo=FALSE, message=FALSE}
library(psych)
colnames(Brand)
Brand$id <- 1:nrow(DATA)
temp <- reshape2::melt(Brand, id.vars=c("attributes","id"),variable.name = "brands", value.name = "val")
temp <- reshape2::dcast(temp, id + brands ~ attributes, value.var = "val")
temp <- temp[,-c(1,2)]
colnames(temp)


scree(temp)
fa <- fa(r = temp, nfactors = 5, rotate = "varimax") 
summary(fa)
fa$loadings #fa outcome

#Scoring
fs <- factor.scores(x = temp,f = fa)

fs$weights

BrandPerception <- BrandPerception[1:140,]
BrandPerception_wide <- reshape2::dcast(BrandPerception, attributes ~ brands, value.var = "val")


brandScores <- colSums(fs$weights * BrandPerception_wide[,2]) #Nike,etc
for (i in 3:11) {
   brandScores <- rbind(brandScores,
                        colSums(fs$weights * BrandPerception_wide[,i])) 
}
rownames(brandScores) <- brands_neworder
brandScores <- data.frame(brandScores)

brandScores$brands <- rownames(brandScores)
brandScores_long <- reshape2::melt(brandScores, id.vars=c("brands"),variable.name = "Factor", value.name = "val")
brandScores_long$brands <- factor(brandScores_long$brands,
                           levels=brands_neworder)

ggplot(data = brandScores_long, aes(y=brands, x=val)) +
  geom_col() + facet_wrap(vars(Factor),scales="free_x") +
  labs(title = "Performance of each brand on each factor")
```

## 2. Meaning of each factor
``` {r FAb2, eval=T, message=FALSE, echo=FALSE, fig.height=8, fig.width=10}
###

plotdata <- data.frame(fs$weights)
plotdata$attributes <- rownames(plotdata)
plotdata <- reshape2::melt(plotdata, id.vars="attributes", value.var = "val")

ggplot(data = plotdata, aes(y=attributes, x=value)) +
  geom_col() + facet_wrap(vars(variable),scales="free_x") +
  labs(title = "Meaning of each factor")
```


## 3. Who likes what
``` {r, eval=T, message=FALSE, fig.height=8, fig.width=10}
# summary(lm(PurchaseCriteria$`03. Heritage 傳統(+) vs Modern 現代(-)` ~
#      Respondent$Region + Respondent$Student + Respondent$Gender + Respondent$Age + Respondent$TotalSpending + Respondent$PurchasePYear))
# 
# X <- data.frame(Respondent$Region, Respondent$Student, Respondent$Gender, Age=Respondent$Age, Respondent$TotalSpending, Respondent$PurchasePYear)
# 
# reg(PurchaseCriteria[,1:5], X,long = T)
# 
# 
# #Brand$Adidas[Brand$attributes==attribute_labels[3]]
#   ggplot(mapping = aes(y=Funnel_long$, x=Respondent$Student)) +
#   geom_violin() # + facet_wrap(vars(Factor),scales="free_x") +
#   #labs(title = "Performance of each brand on each factor")
# 
#   
#   ggplot(mapping = aes(y=Respondent$PurchasePYear, x=X$Age)) +
#   geom_smooth() # + facet_wrap(vars(Factor),scales="free_x") +
#   #labs(title = "Performance of each brand on each factor")
```




```{r analysis2, eval=F}
# Detailed analysis
## PCA
library(factoextra)
#PurchaseCriteria
data.pca <- princomp(PurchaseCriteria)
#summary(data.pca)
fviz_eig(data.pca, addlabels = TRUE)
fviz_pca_var(data.pca, col.var = "black",axes = 1:2)
fviz_cos2(data.pca, choice = "var", axes = 1:2)
fviz_pca_var(data.pca, col.var = "cos2",
            gradient.cols = c("black", "orange", "green"),
            repel = TRUE)
```




``` {r FA, eval=F}
## Pleasing evaluator
BrandPerception_wide <- reshape2::dcast(BrandPerception, brands ~ attributes , value.var = "val")
(BrandPerception_wide)




#distance with brand
brandDistance <- function (test) {
  x <- rbind(test, BrandPerception_wide[,-1])
  result <- as.matrix( stats::dist(x))[-1,1] #column 11
  names(result) <- brands
  result #distance with brand
}
brandDistance <- function (newBrand, user) {
  x <- rbind(user, newBrand, BrandPerception_wide[,-1])
  result <- as.matrix( stats::dist(x))[-1,1] #column 1
  names(result) <- c("new brand",brands)
  result #distance with brand
}
closestBrand <- function (newBrand, user) {
  c("new brand",brands)[which.min(brandDistance(newBrand, user))]
}

#rep(0,14) #test with empty
newBrand <- BrandPerception_wide[1,-1] #test with Nike
newBrand <- round(newBrand,digits=1)
user <- round(newBrand,digits=3)
user <- PurchaseCriteria[3,]

brandDistance(newBrand, user)
closestBrand(newBrand, user)


#distance with user
# x <- rbind(PurchaseCriteria,test)
# result <- as.matrix( stats::dist(x))[-1,1] #column 11
# sum(result)

purchaseDecision <- data.frame()
for (i in 1:length(DATA[,1])){ #for every user
  purchaseDecision <- rbind(purchaseDecision,
                            closestBrand(newBrand,
                                         PurchaseCriteria[i,]
                                         ))
}
purchaseDecision
table(purchaseDecision)

```



``` {r FA2, eval=F}
#FA
library(psych)


scree(PurchaseCriteria)
fa <- fa(r = PurchaseCriteria, nfactors = 5, rotate = "varimax") 
summary(fa)
fa$loadings #fa outcome
#corr(x=PurchaseCriteria)

#Scoring
PurchaseCriteria
fs <- factor.scores(x = PurchaseCriteria,f = fa)
fs
fs$scores
colSums(fs$scores)

#using weights
fs$weights

BrandPerception
BrandPerception_wide <- reshape2::dcast(BrandPerception, attributes ~ brands, value.var = "val")
(BrandPerception_wide)


brandScores <- colSums(fs$weights * BrandPerception_wide[,2]) #Nike,etc
for (i in 3:11) {
   brandScores <- rbind(brandScores,
                        colSums(fs$weights * BrandPerception_wide[,i])) 
}
rownames(brandScores) <- brands
brandScores




# #(All data)
# Brand_long$id <- 1:nrow(DATA)
# Brand_wide <- reshape2::dcast(Brand_long, brands + id ~ attributes, value.var = "val")
# Brand_wide
# 
# fs_nike <- factor.scores(x = Brand_wide[Brand_wide$brands=="Nike",-(1:2)],f = fa)
# fs_nike
# 
# 
# fs_converse <- factor.scores(x = Brand_wide[Brand_wide$brands=="Converse",-(1:2)],f = fa)
# fs_converse
# 
# 
# #(Mean)
# BrandPerception
# BrandPerception_wide <- reshape2::dcast(BrandPerception, brands  ~ attributes, value.var = "val")
# BrandPerception_wide
# BrandPerception_wide <- scale(BrandPerception_wide[,-1])
# factor.scores(x = BrandPerception_wide,f = fa)
# factor.scores(x = BrandPerception_wide[1,-1],f = fa)

## My Extended Analysis

```{r my_new_analysis, echo=TRUE}
# Example: Correlation between price and purchase frequency
cor.test(Respondent$TotalSpending, Respondent$PurchasePYear)

# Or more advanced: visualize brand perception vs. spending
library(ggplot2)
ggplot(PurchaseCriteria, aes(x=`01. High Price 高價(+) vs Low Price 低價(-)`, 
                             y=Respondent$TotalSpending)) +
  geom_point() + geom_smooth(method="lm")




```



```{r head_to_head_chart, echo=FALSE, message=FALSE, warning=FALSE}


# Load necessary libraries
library(dplyr)
library(tidyr)
library(ggplot2)

# Subset Owned and Currently Owned only
own_current_plotdata <- Funnel_long %>%
  filter(type %in% c("1.Owned", "2.CurrentlyOwn"),
         brands %in% c("Nike", "Adidas", "Converse", "NewBalance"))

# Plot grouped bar chart
ggplot(own_current_plotdata, aes(x = type, y = val, fill = brands)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Owned vs Currently Owned Sneakers (4 Brands Only)",
       x = "Stage",
       y = "Average Number of Pairs",
       fill = "Brand") +
  theme_minimal()

# Filter only Consideration data
consider_data <- Funnel_long %>%
  filter(type == "3.Consider", brands %in% c("Nike", "Adidas", "Converse", "NewBalance"))

# Plot horizontal bar chart
ggplot(consider_data, aes(x = val, y = reorder(brands, val), fill = brands)) +
  geom_col() +
  labs(title = "Consideration Rate (Nike, Adidas, Converse, New Balance)",
       x = "Consideration Rate",
       y = "Brand",
       fill = "Brand") +
  theme_minimal()


```
